Efficient Coalition Formation \\ for Web Services

### 2013-06-21 papers/coalition-journal-extension/coalition_journal.tex
Added charts

One way for communities to ensure community stability could be applying a tax, $\epsilon$ ammount of cost for web services changing communities which would make deviation a costly act. However this would require all community coordinators to agree on same ammount of taxtation, being governed by some external entities or web services would join communities with lesser ammount of tax. Another viable solution in our scenario is to stabilize the game using external subsidies. The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain. A community can subside the community with a contant coefficient value of $\lambda$. Rewarding a community with high number of quality participants with $\lambdav(C)$, where $\lambda \leq 1$. This can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable. Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$\cite{eps346856} methods and have been .

Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators. These concepts of applying cost in coallition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.

The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view. It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit. Communities can agree on However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with. To this end, our communities will reward and valuate web services in the community

@@

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments. We created a pool of
web services and populated most of their \emph{QoS} parameters
from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
using Java and executed the simulations on an Intel Xeon X3450
machine with 4GBs of memory. For other parameters missing from the
dataset, we used normal random distribution with parameters
estimated using the method of maximum likelihood.

>>>>

One way for communities to ensure community stability could be applying a tax, $\epsilon$ ammount of cost for web services changing communities which would make deviation a costly act. However this would require all community coordinators to agree on same ammount of taxtation, being governed by some external entities or web services would join communities with lesser ammount of tax. Another viable solution in our scenario is to stabilize the game using external subsidies. The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain. A community master can subside its community with a constant coefficient value of $\lambda$. Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$. Obviously with a big number of $\lambda$ it is always possible to stabilize the community. However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable. Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$\cite{eps346856} methods.

%Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators. These concepts of applying cost in coallition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.

%The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view. It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit. Communities can agree on However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with. To this end, our communities will reward and valuate web services in the community

@@

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments. We created a pool of
web services and populated most of their \emph{QoS} parameters
from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
using Java and executed the simulations on an Intel Xeon X3450
machine with 6GBs of memory. For other parameters missing from the
dataset, we used normal random distribution with parameters
estimated using the method of maximum likelihood.
